Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-10-22 proposalPres.tex

>>>>

%----------------------------------
\begin{frame}{Other Considerations}
  \begin{block}{Factors}
  	\begin{small}
      \begin{itemize}
        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
and driving fatalities and injuries. As a result, people will be able to live longer and
healthier lives. By creating accurate models, we will help advance the development of
autonomous vehicles and make this a reality.
		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle. We will address this by creating a rigorous test plan for our models.
		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
		\item Global Factors: 
		\item Cultural Factors: 
		\item Social Factors: 
		\item Environmental Factors: 
		\item Business Factors: 
		\item Economic Factors: 
      \end{itemize}
     \end{small}
  \end{block}
\end{frame}
